Issues with Dynamical Measurements Across the Disk

### 2019-02-26 paper/ms.tex
Minor fixes

Figure~\ref{fig:midplane} shows the relative $z$ location of the inferred
midplane our imaginary observer would determine as a function of azimuth for
each galaxy, using their local ``solar neighborhood'' (the cylinder defined
above). The $5\textup{--}95$ percentile range from the bootstrap procedure is
shown as the dashed-line error bars. The $90\%$ interquartile range for each
galaxy is $185$, $162$, $84\,\pc$ for \mi{}, \mf{}, and \mm{}. In two of the
three cases the midplane therefore varies by more than $\pm 100$pc depending
on the azimuth along the Solar circle; in the third (\mm{}, which has the
thinnest ``thin disk'' of stars, but the largest stellar mass) the variation
is more like $\pm 50$ pc.

@@

\subsection{LSR Variations} \label{ssec:lsr_var}
We also expect that the local standard of rest (LSR) should vary as a function
of azimuth. We perform this calculation in Appendix~\ref{app:lsr} to estimate
, but performing a best-fit subtraction to correct for misalignment of the
original coordinate system (as in the previous section) is more involved.
Since the variation in the LSR is less pronounced than for the midplane, and
since the dominant effect is limited to $J_r$ (Figure
\ref{fig:many_orbit_wrong_ref}), we defer this calculation to future work.

>>>>

Figure~\ref{fig:midplane} shows the relative $z$ location of the inferred
midplane our imaginary observer would determine as a function of azimuth for
each galaxy, using their local ``solar neighborhood'' (the cylinder defined
above). The $5\textup{--}95$ percentile range from the bootstrap procedure is
shown as the dashed-line error bars. The $90\%$ interquartile range for each
galaxy is $185$, $162$, $84\,\pc$ for \mi{}, \mf{}, and \mm{}. In two of the
three cases the midplane therefore varies by more than $\pm 100\,\pc$
depending on the azimuth along the Solar circle; in the third (\mm{}, which
has the thinnest ``thin disk'' of stars, but the largest stellar mass) the
variation is more like $\pm 50\,\pc$.

@@

\subsection{LSR Variations} \label{ssec:lsr_var}
We also expect that the local standard of rest (LSR) should vary as a function
of azimuth. We perform this calculation in Appendix~\ref{app:lsr} to estimate
, but performing a best-fit subtraction to correct for misalignment of the
original coordinate system (as in the previous section) is more involved.
Since the variation in the LSR is less pronounced than for the midplane, and
since the dominant effect is limited to $J_r$
(Figure~\ref{fig:many_orbit_wrong_ref}), we defer this calculation to future
work.
